Hypotheses

### 2019-09-26 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Working on the four basic plots. Need to figure out how to specify different covariates.

@@

```{r}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

@@

```{r}

@@

# Hypotheses:
# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

>>>>

#### In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

```{r overall, echo = FALSE, warning = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

@@

We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors. Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.

```{r relationship-with-gov, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 1, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

@@

We theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.

#### 1. Managerial Practices

```{r managerial-practices, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == c( "Financial transparency: Yes",
  "Accountability: Yes")) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

#### 2. Funding Sources
```{r funding_sources, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels ==   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

#### 3. Issue Areas

```{r issue-areas, echo = FALSE, warning = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
    ggplot(aes(x = Theta, y = levels, fill = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

@@
